Applying Computational Intelligence Methods for Predicting the Sales of Newly Published Books in a Real Editorial Business Management Environment

### 2016-09-07 paper.tex
Another paragraph reviewed and commented in the introduction.

Within the general area of cultural products, the problem of
predicting sales is specially acute for book publishers, who, among other
providers of content in physical form, release new {\em products} more frequently than
other industries, so that they face the problem of predicting sales quite often. The issue, in this case, is to print an adequate number of copies but not too many, as the unsold volumes will lead to losses and sunk inventory cost, 
whereas if the number of printed copies was not enough, a new print
run can always be made, resulting in temporary losses due to a lack of supply
or in bad marketing for the customers, for instance. However, in
practice predicting lower sales than the actual ones is not such a big
problem because when inventory is close to exhaustion new print runs
are made; however, this new print run presents the same problem as the
initial one of printing only as many as forecasted, although its cost
is not as high as the initial one and we are not so concerned with
this issue in this paper.

>>>>

Within the general area of cultural products, the problem of
predicting sales is specially acute for book publishers who, among other
providers of content in physical form, release new {\em products} more frequently than
other industries, so that they face the problem of predicting sales quite often. The issue, in this case, is to print an adequate number of copies but not too many, as the unsold volumes will lead to losses and sunk inventory cost, 
whereas if the number of printed copies was not enough, a new print
run can always be made, resulting in temporary losses due to a lack of supply
or in bad marketing for the customers, for instance. However, in
practice predicting lower sales than the actual ones is not such a big
problem because when inventory is close to exhaustion new print runs
are made; % (Paloma) I think that the thing that should be highlighted here is that is not big deal because the print run is made _before_ the inventory is exhausted. I mean, the sentence highlights the fact that a new print run is made, and not that maybe the situation where there's any book never happens. 
% Suggestion:  However, in practice predicting lower sales than the actual ones is not such a big problem because the new print run is orderer before the inventory is exhausted;
 nevertheless, this new print run presents the same problem as the
initial one of printing only as many as forecasted, although its cost
is not as high as the initial one 
% (Paloma) Should we really say this next sentence? :\
and we are not so concerned with
this issue in this paper.
